---
title: "Assignment 10"
author: "NAME, NetID"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

*This is an **individual** assignment.*

The objective of this assignment is to give you experience composing programs in R with an emphasis on using Tidyverse packages.

Please meet the specific requirements exactly. Do not change or remove any of the instructions; just add you name and NetID in the author metadata area above and code in the code cells as indicated (you may edit/remove the "TODO" comments).  Please make sure to test your programs before submitting your solutions on Canvas!

## Problem 1: Marketing Campaign Analysis

The file `marketing_campaigns.csv` contains data about a series of marketing campaigns; the first five lines of the file are shown below.

```
Date,Campaign,Impressions,Clicks
2023-03-31,Campaign A,647,14
2023-04-01,Campaign A,639,11
2023-04-02,Campaign A,532,14
2023-04-03,Campaign A,487,8
```

First, load the tidyverse package and the data.

```{r problem1a}
# TODO: Insert your code here
```
Next, calculate CTR using the Tidyverse `mutate` method.

```{r problem1b}
# TODO: Calculate CTR
```

Finally, use the tidyverse methods `group_by`, `summarize`, and `filter` to produce an Nx2 tibble of all the campaigns with an average CTR > 0.02.  Your output should have the following format (with the ?'s being replaced with letters for the campaigns and numbers elsewhere).  You don't need to write this out to a file; just print it out in your R Markdown output.

```
## # A tibble: ? × 2
##   Campaign   avg_CTR
##   <chr>        <dbl>
## 1 Campaign ?  0.0???
## 2 Campaign ?  0.0???
##       ...
```

```{r problem1c}
# TODO: Filter campaigns with CTR > 0.02
```


## Problem 2: Manipulating Product Data

You have a product data `products.csv` with the following columns: `Item`, `Retail.Price` and `Unit.Cost`; first, load this data.

```{r problem2a}
# TODO: Load the data
```

Now use the `mutate` method to create a new column `Margin` using the formula Margin = (Retail.Price - Unit.Cost) / Retail.Price).

```{r problem2b}
# TODO: Calculate Margin
```

Use the `separate` method to separate the "Item" column into "Item" and "Category" columns using the space-padded hyphen as a separator (`" - "`).

```{r problem2c}
# TODO: Separate Item into Item and Category
```

Finally, calculate the average Margin for each Category and write the resulting data out to `avg_margin_by_category.csv`.  The first five lines of this file should appear as follows.

```
Category,avg_Margin
Backpacks,0.152980205100494
Belt Buckles,0.17708841870366
Belts,0.159983304991489
Boots,0.157098313776764
```

```{r problem2d}
# TODO: Calculate average Margin per Category and write out to avg_margin_by_category.csv
```
